Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-19 paper/main.tex
paper updates

@@

In each case the most effective model we trained was a decision tree. (The other
models we tried were Logistic Regression and MLP. Yaoyuan - anything to add to
this section?)

@@

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Size-P & Contextual (Syntactic) & 0.112624 \\
F-Stmt-Constr-C3= & Contextual (Syntactic) & 0.061552 \\
F-Expr-Constr-P=List & Contextual (Syntactic) & 0.054632 \\
F-PythonBlame & Dynamic (Error location) & 0.039189 \\
F-Type=unknown & Dynamic (Type) & 0.037390 \\
F-Type-P=unknown & Contextual (Type) & 0.037330 \\
F-PythonMsg=IndexError & Dynamic (Error message) & 0.032749 \\
F-Size & Syntactic & 0.028203 \\
F-Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.026663 \\
F-Size-C1 & Contextual (Syntactic) & 0.023662 \\
F-Expr-Constr=Var & Syntactic & 0.020390 \\
F-Type-C1=unknown & Contextual (Type) & 0.019815 \\
\end{tabular}
\caption{Based on the Top-3 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF.}
\label{tab:feature-predictive-power}
\end{table}

@@

>>>>

\emph{Models} The following descriptions of Logistic Regression, Decision Trees,
and MLP will have to be redone as they are copied from Learning to Blame.

\emph{Logistic Regression}
The simplest classifier we investigate is logistic regression:
a linear model where the goal is to learn a set of weights $W$
that describe the following model for predicting a label
$b$ from a feature vector $v$:
%
\[ \Pr(b = 1 | v) = \frac{1}{1 + e^{-W^{\top} v}} \]
%
The weights $W$ are learnt from training data, and the value of
$\Pr(b | v)$ naturally leads to a confidence score $\mathcal{C}$.
%
Logistic regression is a widely used classification algorithm, preferred
for its simplicity, ease of generalization, and interpretability.
%
Its main limitation is that the prediction rule is constrained to be a
linear combination of the features, and hence relatively simple.
%
While this can be somewhat mitigated by adding higher order (quadratic
or cubic) features, this often requires substantial domain knowledge.

\emph{Decision Trees}
Decision tree algorithms learn a tree of binary predicates over the
features, recursively partitioning the input space until a final
classification can be made.
%
Each node in the tree contains a single predicate of the form
$v_j \leq t$ for some feature $v_j$ and threshold $t$, which determines
whether a given input should proceed down the left or right subtree.
%
Each leaf is labeled with a prediction and the fraction of
correctly-labeled training samples that would reach it; the latter
quantity can be interpreted as the decision tree's confidence in its
prediction.
%
This leads to a prediction rule that can be quite expressive depending
on the data used to build it.

Training a decision tree entails finding both a set of good partitioning
predicates and a good ordering of the predicates based on data.
%
This is usually done in a top-down greedy manner, and there are several
standard training algorithms such as C4.5 \cite{Quinlan1993-de} and
CART \cite{Breiman1984-qy}.

Another advantage of decision trees is their ease of interpretation ---
the decision rule is a white-box model that can be readily described to
a human, especially when the tree is small.
%
However, the main limitation is that these trees often do not generalize
well, though this can be somewhat mitigated by \emph{pruning} the tree.

\emph{Neural Networks}
%
The last (and most complex) model we use is a type of neural network
called a \emph{multi-layer perceptron} (see \cite{Nielsen2015-pu} for
an introduction to neural networks).
%
A multi-layer perceptron can be represented as a directed acyclic
graph whose nodes are arranged in layers that are fully connected by
weighted edges.
%
The first layer corresponds to the input features, and the final to the
output.
%
%The output of a node $v$ in an internal layer is given by:
The output of an internal node $v$ is
%
\[ h_v = g(\sum_{j \in N(v)} W_{jv} h_j ) \]
%
where $N(v)$ is the set of nodes in the previous layer that are adjacent
to $v$, $W_{jv}$ is the weight of the $(j, v)$ edge and $h_j$ is the
output of node $j$ in the previous layer.
%
Finally $g$ is a non-linear function, called the activation function,
which in recent work is commonly chosen to be the \emph{rectified linear
  unit} (ReLU), defined as $g(x) = \mathsf{max}(0,x)$
\cite{Nair2010-xg}.
%
The number of layers, the number of neurons per layer, and the
connections between layers constitute the \emph{architecture} of a
neural network.
%
In this work, we use relatively simple neural networks which have an
input layer, a single hidden layer and an output layer.

A major advantage of neural networks is their ability to discover
interesting combinations of features through non-linearity, which
significantly reduces the need for manual feature engineering, and
allows high expressivity.
%
On the other hand, this makes the networks particularly difficult to
interpret and also difficult to generalize unless vast amounts of
training data are available.

@@

In each case the most effective model we trained was a decision tree. (The other
models we tried were Logistic Regression and MLP. Yao-Yuan - anything to add to
this section? in particular, is it actually accurate to say we're doing
cross-validation - the 3-fold thing we do is actually just to select parameters,
and then there's no cross-validation on the final model, right?)

@@

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Size-P & Contextual (Syntactic) & 0.112624 \\
F-Stmt-Constr-C3= & Contextual (Syntactic) & 0.061552 \\
F-Expr-Constr-P=List & Contextual (Syntactic) & 0.054632 \\
F-PythonBlame & Dynamic (Error location) & 0.039189 \\
F-Type=unknown & Dynamic (Type) & 0.037390 \\
F-Type-P=unknown & Contextual (Type) & 0.037330 \\
F-PythonMsg=IndexError & Dynamic (Error message) & 0.032749 \\
F-Size & Syntactic & 0.028203 \\
F-Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.026663 \\
F-Size-C1 & Contextual (Syntactic) & 0.023662 \\
F-Expr-Constr=Var & Syntactic & 0.020390 \\
F-Type-C1=unknown & Contextual (Type) & 0.019815 \\
\end{tabular}
\caption{Based on the Top-3 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF. TODO: base on Top-1 instead?}
\label{tab:feature-predictive-power}
\end{table}

To measure how important each feature is, we use Gini Importance. In a decision
tree,

@@

\subsection{Threats to validity}

\emph{Overfitting and other machine learning issues} Yao-Yuan, how do we avoid
these?

\emph{Language choice} We only showed that this technique works for Python 3.
However, \cite{learning-to-blame} uses a similar technique to great effect in
OCaml, and if it works on these two quite-different languages then we believe
it would work on others as well. Additionally, Python is a common choice of
language for introductory programming courses, so even a technique that worked
only on Python would still be very useful for helping novices.

\emph{Target population} We don't know exactly who our study population is -
who wrote the programs in the dataset and what exactly they were trying to write.
It is likely that they are primarily students and not professional software engineers,
and thus possible that our technique does not generalize well to the kinds of
bugs that would be found in an industrial setting rather than an educational one.

\emph{Automatic labeling} Since our dataset is so large, we were forced to use an automatic
scheme to label bugs rather than marking them by hand. We chose to use the diffs
between each program that crashes and the next program that does not, but this method
is not 100\% accurate because the next program may contain additional changes
beyond what was needed to fix the bug, or it may indeed be an entirely unrelated
program. We mitigate this problem by discarding as outliers program pairs that have
changed too much. We also note that if our `true' accuracy is indeed a little
smaller than our reported accuracy because of this effect, then the `true' baseline
is also lower than the reported baseline for the same reason, so our
\emph{margin} of effectiveness is unlikely to change much.
